---
title: "Thyroid dashboard"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: https://gitlab.com/Abdellah-Laassairi/thyroid-disease-analysis
    theme: 
      version: 4
      bootswatch: united
---

```{r setup, include=FALSE, context = "server"}
library(flexdashboard)
library(shiny)
library(shinyWidgets)
library(glue)
library(stringr)
library(ggplot2)
library(dplyr)
library(plotly)
library(simputation)
library(insight)
library(data.table)
library(qwraps2)
library(rmarkdown)
library(DT)
library(dplyr)
library(splitstackshape)
library(ggthemes)
library(purrr)
library(tidyr)
library(naniar)
library(fmsb)

```

# Sidebar {.sidebar}

```{r}
# Preprocessing the data

raw_data=read.csv("/home/odeck/Desktop/SDR/Project/data/thyroid.csv")

raw_data$ThryroidClass=as.factor(raw_data$ThryroidClas)
categorical_cols=c('patient_gender','presc_thyroxine','queried_why_on_thyroxine','presc_anthyroid_meds','sick','pregnant',
              'radioactive_iodine_therapyI131','query_hyperthyroid','lithium','goitre','tumor'
              
              ,
              'hypopituitarism','psych_condition','TSH_measured','T3_measured','T4_measured','thyrox_util_rate_T4U_measured','FTI_measured'
              
              )

numerical_cols=c('patient_age','TSH_reading','T3_reading','T4_reading','thyrox_util_rate_T4U_reading','FTI_reading')


raw_data$patient_age<-as.numeric(raw_data$patient_age)
raw_data$FTI_reading<-as.numeric(raw_data$FTI_reading)

raw_data[categorical_cols] <- lapply(raw_data[categorical_cols], factor)
raw_data<-subset(raw_data, select = -c(ref_src))

#



```

```{r}
# Define inputs
selectInput('input_imputation', label = 'Select Imputation', choices = c('None','impute_cart', 'impute_median'=0, 'impute_rlm'=1,'impute_lm'), selected = 'None')

selectInput('input_gender', label = 'Select Gender', choices = c('Both'=-1, 'Male'=0, 'Female'=1), selected = 'All')

sliderInput('input_age', label = 'Select Age Range', min = 0, max = 120, value = 50, 
            step = 1)

awesomeCheckboxGroup(
   inputId = "sick",
   label = "Select if patient is sick : ", 
    choices =  c("Sick"=1, "negative"=0),
   inline = FALSE, 
    status = "danger"
)

awesomeCheckboxGroup(
   inputId = "tumor",
   label = "Select if patient has tumor : ", 
    choices =  c("True"=1, "False"=0),
   inline = FALSE, 
    status = "danger"
)




```

```{r}
# Reactive DataFrame based on the inputs

reactive_df_imputed <- reactive(
    if(input$input_imputation!="impute_cart")
      raw_data<-impute_cart(raw_data, patient_age+TSH_reading+FTI_reading+T3_reading+T4_reading+thyrox_util_rate_T4U_reading ~ ., add_residual = "normal")
    else 
      if(input$input_imputation!="impute_lm")
        raw_data<-impute_lm(raw_data, patient_age+TSH_reading+FTI_reading+T3_reading+T4_reading+thyrox_util_rate_T4U_reading ~ patient_gender+goitre+tumor+sick, add_residual = "normal")
      else
         if(input$input_imputation!="impute_rlm")
            raw_data<-impute_rlm(raw_data,patient_age+ TSH_reading+FTI_reading+T3_reading+T4_reading+thyrox_util_rate_T4U_reading ~ patient_gender+goitre+tumor+sick, add_residual = "normal")
         else
            raw_data<-impute_mean(raw_data,patient_age+ TSH_reading+FTI_reading+T3_reading+T4_reading+thyrox_util_rate_T4U_reading ~ patient_gender, add_residual = "normal")
)

reactive_df_NA <-reactive(
   if(length(input$sick)==1)
      if (length(input$tumor)==1 )
          
          if(input$input_gender==-1)
            raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age,tumor==input$tumor, sick==input$sick )
          else
            raw_data<-raw_data %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor,sick==input$sick )
      
        else
              
          if(input$input_gender==-1)
            raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age,sick==input$sick  )
          else
            raw_data<-raw_data %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,sick==input$sick )
    else 
      
      if (length(input$tumor)==1 )
        
        if(input$input_gender==-1)
          raw_data<-raw_data %>% 
          filter(patient_age <= input$input_age,tumor==input$tumor )
        else
          raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor)
    
      else
            
        if(input$input_gender==-1)
          raw_data<-raw_data %>% 
          filter(patient_age <= input$input_age )
        else
          raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender)
)

reactive_df_NA <- reactive(
    if(length(input$sick)==1)
      if (length(input$tumor)==1 )
          
          if(input$input_gender==-1)
            raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age,tumor==input$tumor, sick==input$sick )
          else
            raw_data<-raw_data %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor,sick==input$sick )
      
        else
              
          if(input$input_gender==-1)
            raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age,sick==input$sick  )
          else
            raw_data<-raw_data %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,sick==input$sick )
    else 
      
      if (length(input$tumor)==1 )
        
        if(input$input_gender==-1)
          raw_data<-raw_data %>% 
          filter(patient_age <= input$input_age,tumor==input$tumor )
        else
          raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor)
    
      else
            
        if(input$input_gender==-1)
          raw_data<-raw_data %>% 
          filter(patient_age <= input$input_age )
        else
          raw_data<-raw_data %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender)
  )

reactive_df <- reactive(
  if(input$input_imputation!="None")
   if(length(input$sick)==1)
      if (length(input$tumor)==1 )
          
          if(input$input_gender==-1)
            raw_data<-  reactive_df_imputed() %>% 
            filter(patient_age <= input$input_age,tumor==input$tumor, sick==input$sick )
          else
            raw_data<-reactive_df_imputed() %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor,sick==input$sick )
      
        else
              
          if(input$input_gender==-1)
            raw_data<-reactive_df_imputed() %>% 
            filter(patient_age <= input$input_age,sick==input$sick  )
          else
            raw_data<-reactive_df_imputed() %>% 
              filter(patient_age <= input$input_age, patient_gender==input$input_gender,sick==input$sick )
    else 
      
      if (length(input$tumor)==1 )
        
        if(input$input_gender==-1)
          raw_data<-reactive_df_imputed() %>% 
          filter(patient_age <= input$input_age,tumor==input$tumor )
        else
          raw_data<-reactive_df_imputed() %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender,tumor==input$tumor)
    
      else
            
        if(input$input_gender==-1)
          raw_data<-reactive_df_imputed() %>% 
          filter(patient_age <= input$input_age )
        else
          raw_data<-reactive_df_imputed() %>% 
            filter(patient_age <= input$input_age, patient_gender==input$input_gender)
            
  else
    raw_data<-reactive_df_NA()
   
  )

```

# Patients

## Row {data-height="120"}

### Number of patients

```{r}
renderValueBox(
valueBox(nbPatients <-nrow(reactive_df()), icon = "fa-user-md")
)

```

### Number of patients with Thyroid disease

```{r}
renderValueBox(
valueBox(nrow(reactive_df()[reactive_df()$ThryroidClas == "sick", ]), icon = "fa-heartbeat")
)
```

### Number of features

```{r}
renderValueBox(
valueBox(nbPatients <-ncol(reactive_df()), icon = 'fas fa-stethoscope')
)
```

## Row {data-height="300"}

### Selected patients 
```{r}

renderPlotly({
  selected <- input$responses_rows_selected
  data<-reactive_df()[selected,]
  fig <- plot_ly(
      type = 'scatterpolar',
      fill = 'toself'
    ) 

  data = subset(data, select = numerical_cols)

  if(nrow(data)>0)
   for(i in 1:nrow(data)){
      fig <- fig %>%
        add_trace(
          r = unname(slice(data, i)),
          theta = numerical_cols,
          name = paste('Patient',i)
        ) 
 }
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,100)
      )
    )
  )%>% config(displayModeBar = F)
fig
})
```

### Categorical features of selected patients
```{r}

renderPlotly({
  selected <- input$responses_rows_selected
  data<-reactive_df()[selected,]
  fig <- plot_ly(
      type = 'scatterpolar',
      fill = 'toself'
    ) 

  data = subset(data, select = categorical_cols)
  print(data)

  if(nrow(data)>0)
   for(i in 1:nrow(data)){
      print("inside")
      print(unname(slice(data, i)
))
      fig <- fig %>%
        add_trace(
          r = unname(slice(data, i)),
          theta = categorical_cols,
          name = paste('Patient',i)
        ) 
 }
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,1)
      )
    )
  )%>% config(displayModeBar = F)
fig
})
```
## Row {data-height="700"}

### All patients (Imputed or missing values are colored in red)

```{r}
DT::dataTableOutput("responses")
output$responses <- DT::renderDataTable(

reactive_df() %>%
  datatable(options = list(
    pageLength=9
  ),
            class = "cell-border compact hover order-column")%>% formatStyle(names(reactive_df()), backgroundColor = styleEqual(c(NA), c('rgb(255,63,63)')))

)
```

# Analysis
## Row {data-height="120"}

### Number of Variables with missing values

```{r}
 
calculate<- function(df){
  
  n<-0
  for(i in 1:ncol(sapply(df, function(x) is.na(x)))){
    if (sum(sapply(df, function(x) is.na(x))[,i])>0)
      n<-n+1
  }
  return(n)
}

renderValueBox(

valueBox(calculate(reactive_df()), icon = "fas fa-database")
)

```

### Number of missing observations

```{r}
renderValueBox(
valueBox(n_miss(reactive_df()), icon = "fa fa-square-o")
)
```

### Number of complete observations

```{r}
renderValueBox(
valueBox(nbPatients <-n_complete(reactive_df()), icon = 'fa fa-check-square-o')
)
```


## Row {data-height="370"}

### Missing values across factors
```{r}
renderPlotly({
  #p<-gg_miss_upset(reactive_df())
  #ggplotly(p)%>% config(displayModeBar = F)
  p<-gg_miss_fct(reactive_df(), patient_gender)+ #(title = paste("NA in Thyroid data and","patient_gender"))+
     theme(axis.title.y=element_blank(),
        #axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  ggplotly(p)%>% config(displayModeBar = F)



})
```

### Missing  values for each variable
```{r}
renderPlot({
  gg_miss_var(reactive_df())
})
```

## Row {data-height="100"}

```{r}

tags$h3("Analysis and summary of different variables")

```

## Row {data-height="400"}

### Numerical Variable :

```{r}

renderPlotly({
data<-reactive_df()%>% bind_shadow()

p<-ggplot(data,aes_string(x=input$input_numerical,color=input$input_numerical,fill=input$input_1))+
            geom_histogram(aes(y=..density..),alpha=0.5,position="identity")+
            geom_density(alpha=.2)+theme_gdocs()
ggplotly(p)%>% config(displayModeBar = F)
})

```


### Insights

```{r}

selectInput('input_numerical', label = 'Select Numerical variable', choices = numerical_cols, selected = 'patient_age')

choices =c(categorical_cols,as.character(sapply(numerical_cols, function(x) paste(x,"_NA", sep=""))))
selectInput('input_1', label = 'Select Group by variable', choices = choices, selected = 'patient_gender')

id='name'
value=sum(is.na(raw_data$patient_age))
total=nrow(raw_data)
title= 'Percentage of missing values (NAs) :'
progressBar(
  id,
  value,
  total = total,
  display_pct = TRUE,
  size = 100,
  status = "warning",
  striped = TRUE,
  title = title,
  commas = TRUE,
  unit_mark = "%"
)

rename_dataframe <- function(df, name) {
  colnames(df) <- name
  return(df)
}

header.true <- function(df) {
  colnames(df) <- df[1,]
  df <- df[-1, ] 
  rownames(df) <- NULL

  return(df)
}

renderDT(
reactive_df()%>%select(input$input_numerical) %>%summary()%>%
  list() %>%do.call(what=cbind)%>% data.frame()%>%      rename_dataframe(input$input_numerical)%>%cSplit(input$input_numerical, ":")%>%
  rename_dataframe(c('Summary', 'Values'))%>%t() %>%data.frame()%>%header.true()%>%

  
  datatable(
    options = list(dom = 't'),
    rownames= FALSE,

    class = "cell-border compact hover order-column")

) 

```

## Row {data-height="350"}

### Categorical Variable :

```{r}

renderPlotly({
data<-reactive_df()%>% bind_shadow()

p<-ggplot(data=data,aes_string(x=input$input_categorical, color=input$input_2, fill=input$input_2))+
            geom_bar(aes(y=(..count..)),alpha=0.5,position="identity")+theme_gdocs()
ggplotly(p)%>% config(displayModeBar = F)
})
```

### Insights

```{r}
selectInput('input_categorical', label = 'Select Categorical variable', choices = categorical_cols, selected = 'patient_gender')

choices =c(categorical_cols,as.character(sapply(categorical_cols, function(x) paste(x,"_NA", sep=""))))

selectInput('input_2', label = 'Select Group by variable', choices = choices, selected = 'patient_gender')

id='name'
value=sum(is.na(raw_data$patient_gender))
total=nrow(raw_data)

title= 'Percentage of missing values (NAs) :'
progressBar(
  id,
  value,
  total = total,
  display_pct = TRUE,
  size = 20,
  status = "warning",
  striped = FALSE,
  title = title,
  commas = TRUE,
  unit_mark = "%"
)
renderDT(
reactive_df()%>%select(input$input_categorical) %>%summary()%>%
  list() %>%do.call(what=cbind)%>% data.frame()%>%      rename_dataframe(input$input_categorical)%>%cSplit(input$input_categorical, ":")%>%
  rename_dataframe(c('Summary', 'Values'))%>%t() %>%data.frame()%>%header.true()%>%

  
  datatable(
    options = list(dom = 't'),
    rownames= FALSE,

    class = "cell-border compact hover order-column")

)


```


# Comparison

## Row {data-height="100"}

```{r}

tags$h3("Comparaison between Population A and B : ")

```
## Row {data-height="320"}


### Population A : 

```{r}
fillCol(height = 300, flex = c(NA, 1), 
  inputPanel(
    dropdown(
      
      pickerInput(inputId = 'compare_variable',
            label = 'Select Variable',
            choices = categorical_cols,
            selected = "patient_gender",
            options = list(`style` = "btn-warning")),

      pickerInput(inputId = 'group_variable',
                  label = 'Group by',
                  choices = categorical_cols,
                  selected="pregnant",
                  options = list(`style` = "btn-info")),
  

  
      style = "unite", icon = icon("gear"),
      status = "danger", width = "300px",
      animate = animateOptions(
        enter = animations$fading_entrances$fadeInLeftBig,
        exit = animations$fading_exits$fadeOutRightBig
      )
    ),
  
  ),
  plotOutput("populationA", height = "100%")
)

output$populationA <- renderPlot({

ggplot(data=reactive_df(),aes_string(x=input$compare_variable,color=input$group_variable,fill=input$group_variable))+
    geom_bar(aes(y=(..count..)),alpha=0.5,position="identity")+theme_light()
})



```
### Population B : 

```{r}
fillCol(height = 300, flex = c(NA, 1), 
  inputPanel(
    dropdown(
      
      pickerInput(inputId = 'compare_variable2',
            label = 'Select Variable',
            choices = categorical_cols,
            selected = "patient_gender",
            options = list(`style` = "btn-warning")),

      pickerInput(inputId = 'group_variable2',
                  label = 'Group by',
                  choices = categorical_cols,
                  selected="sick",
                  options = list(`style` = "btn-info")),
  

  
      style = "unite", icon = icon("gear"),
      status = "danger", width = "300px",
      animate = animateOptions(
        enter = animations$fading_entrances$fadeInLeftBig,
        exit = animations$fading_exits$fadeOutRightBig
      )
    ),
  
  ),
  plotOutput("populationB", height = "100%")
)

output$populationB <- renderPlot({

ggplot(data=reactive_df(),aes_string(x=input$compare_variable2,color=input$group_variable2,fill=input$group_variable2))+
    geom_bar(aes(y=(..count..)),alpha=0.5,position="identity")+theme_light()
})



```


## Row {data-height="300"}


### Population C : 

```{r}
fillCol(height = 300, flex = c(NA, 1), 
  inputPanel(
    dropdown(
      
      pickerInput(inputId = 'compare_variable_n',
            label = 'Select Variable',
            choices = numerical_cols,
            selected = "patient_gender",
            options = list(`style` = "btn-warning")),

      pickerInput(inputId = 'group_variable_n',
                  label = 'Group by',
                  choices = categorical_cols,
                  selected="pregnant",
                  options = list(`style` = "btn-info")),
  
      style = "unite", icon = icon("gear"),
      status = "danger", width = "300px",
      animate = animateOptions(
        enter = animations$fading_entrances$fadeInLeftBig,
        exit = animations$fading_exits$fadeOutRightBig
      )
    ),
  
  ),
  plotOutput("populationC", height = "100%")
)

output$populationC <- renderPlot({

ggplot(reactive_df(),aes_string(x=input$compare_variable_n,color=input$group_variable_n,fill=input$group_variable_n))+
            geom_histogram(aes(y=..density..),alpha=0.5,position="identity")+
            geom_density(alpha=.2)+theme_gdocs()
})



```
### Population D : 

```{r}
fillCol(height = 300, flex = c(NA, 1), 
  inputPanel(
    dropdown(
      
      pickerInput(inputId = 'compare_variable_n_2',
            label = 'Select Variable',
            choices = numerical_cols,
            selected = "patient_gender",
            options = list(`style` = "btn-warning")),

      pickerInput(inputId = 'group_variable_n_2',
                  label = 'Group by',
                  choices = categorical_cols,
                  selected="sick",
                  options = list(`style` = "btn-info")),
  

  
      style = "unite", icon = icon("gear"),
      status = "danger", width = "300px",
      animate = animateOptions(
        enter = animations$fading_entrances$fadeInLeftBig,
        exit = animations$fading_exits$fadeOutRightBig
      )
    ),
  
  ),
  plotOutput("populationD", height = "100%")
)

output$populationD<- renderPlot({

ggplot(reactive_df(),aes_string(x=input$compare_variable_n_2,color=input$group_variable_n_2,fill=input$group_variable_n_2))+
            geom_histogram(aes(y=..density..),alpha=0.5,position="identity")+
            geom_density(alpha=.2)+theme_gdocs()
})



```
